---
title: Example R Markdown document
author: Karl Broman
date: 2017-03-23
output: html_document
---

This is an example R Markdown document, which allows a mixture of text
and R code. When processed, the R code is executed and output (for
example, a graph) is inserted.

I'll first load the "tidy" version of the data from Activity 1. I'll
download the file using `download.file` and then load it into R using
`read.csv`. (I use the `method="libcurl"` business because the URL is
being redirected. The `file.exists` business ensures that we download
the file just once.)

```{r load_data}
url <- "http://bit.ly/StPaul-1-tidy"
file <- "tidy.csv"
if(!file.exists(file)) {
    download.file(url, file, method="libcurl")
}
dat <- read.csv(file)
```

The dataset has `r nrow(dat)` rows and `r ncol(dat) columns.
Here are the first few rows:

```{r head_data}
head(dat)
```

Here's a plot:

```{r set_seed, echo=FALSE}
set.seed(57245016)
```

```{r plot_data}
library(ggplot2)
ggplot(dat, aes(x=genotype, y=response)) +
    geom_jitter(position=position_jitter(0.08)) +
    facet_grid(treatment_time ~ strain)
```
